\documentclass{article}

\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    urlcolor=blue,
}

\begin{document}

\title{Bookstore: Initial Report}
\author{
Omar Emara (20180364), Mohamed Alkhateb (20180470), \\
Karim Ashraf (20180424), Mohamed Fathy (20180524), \\
Mahmoud Mohamed (20180571), Medhat Taha (20180575)
}
\maketitle

\begin{abstract}
This report describes the general plan for the Bookstore project.
We start by defining the general idea behind the project.
Then we outline the core functionality that the project should implement.
Next we list some of the services available in the market that implements the same functionality.
Lastly we introduce the technology stack of our choice.
\end{abstract}

\section{Idea}

The \emph{Bookstore} project is an implementation of an online platform providing the service of
commercial trading of electronic books. It is tailored to authors, publishers, booksellers, and
customers. The end user can sell and buy books through the platform. Full administrative control
over the platform is provided.

\section{Functionality}

The platform provides the following functionalities:

\begin{itemize}
\item Users can register an account using their name, email, and password.
\item Users can login using their email and password.
\item Users can browse the available books and add them to their cart.
\item Users can checkout their cart using their preferred payment method.
\item Users can view the orders they previously made.
\item Users can view the customers who ordered their books.
\item Users can add and upload a book to be sold.
\item Administrators can view all the registered users.
\item Administrators can view all the orders in the system.
\end{itemize}

\section{Market Study}

Similar services are listed below:

\begin{itemize}
\item \href{https://www.goodreads.com/}{Good Reads}.
\item \href{https://www.amazon.com/books}{Amazon Books}.
\item \href{https://bookoutlet.com/}{Book Outlet}.
\item \href{https://www.bookdepository.com/}{Book Depository}.
\end{itemize}

\section{Technology Stack}

\begin{itemize}
\item DBMS : PostgreSQL
\item GraphQL Server : PostGraphile
\item Web Server : NGINX
\item Server-Side Renderer: PHP
\item GraphQL Client : GraphQL PHP
\item UI Framework: MDC Web
\end{itemize}

\end{document}
